\section{Results}
\label{sec:results}

\subsection{Cluster Structure}

K-means clustering with $k = 6$ (selected by elbow method on within-cluster inertia)
partitions the 20-game validation corpus into six clusters. Table~\ref{tab:clusters}
summarises each cluster with its centroid coordinates $(T, I, G, E, R)$ and member games.

\begin{table}[h]
\centering
\caption{K-means clusters in TIGER space ($k=6$, 20-game validation corpus).}
\label{tab:clusters}
\begin{tabular}{llp{5.5cm}}
\hline
\textbf{Cluster} & \textbf{Centroid $(T,I,G,E,R)$} & \textbf{Members} \\
\hline
C0 (singleton) & (2.8, 5.9, 1.9, 8.4, 7.4) & Codenames \\
C1 (light social) & (5.0, 6.0, 2.7, 8.4, 5.9) & Crokinole, Love Letter, Skull, Hanabi, Cant Stop, Hive \\
C2 (high-pressure) & (7.1, 6.8, 4.6, 7.3, 6.7) & Pandemic, Chess \\
C3 (gateway Euro) & (5.9, 6.1, 4.9, 6.3, 5.7) & Catan, Secret Hitler, HAUL \\
C4 (heavy Euro) & (7.0, 5.5, 7.3, 5.0, 7.4) & Agricola, Brass: Birmingham, Spirit Island, CRUCIBLE \\
C5 (elegant medium) & (3.7, 4.2, 5.3, 7.3, 6.8) & Azul, Dominion, 7 Wonders, Concordia \\
\hline
\end{tabular}
\end{table}

Three observations stand out. First, Codenames (C0) is a singleton at distance $> 4.0$
from all other cluster centres, confirming that its combination of low Game-Architecture
($G = 1.9$), high Elegance ($E = 8.4$), and high Range ($R = 7.4$) is architecturally
isolated in the corpus. Second, Pandemic and Chess (C2) share a cluster with centroid
$(7.1, 6.8, 4.6, 7.3, 6.7)$ despite belonging to entirely different genres, suggesting
that high Tension and high Interaction with moderate Architecture constitute a structural
equivalence class. Third, the heavy-Euro cluster (C4) is the only cluster where
Game-Architecture ($G \approx 7.3$) consistently exceeds Elegance ($E \approx 5.0$),
confirming Lacerda's complexity stack as a recognisable fingerprint pattern.

\subsection{Sparse Region Identification}

Gaussian kernel density estimation (bandwidth $= 1.5$ in standardised TIGER coordinates)
identifies four TIGER space coordinates in the bottom-quartile density range. These
are translated into design briefs (Table~\ref{tab:gaps}).

\begin{table}[h]
\centering
\caption{Four sparse design regions identified in TIGER space.}
\label{tab:gaps}
\begin{tabular}{llp{4.5cm}}
\hline
\textbf{Gap} & \textbf{TIGER $(T,I,G,E,R)$} & \textbf{Design character} \\
\hline
G1: High-Tension Elegant Light & $(8, 4, 2, 9, 5)$ & Punishing push-your-luck or time-pressure with minimal rules; learnable in 5 minutes \\
G2: High-Interaction Low-Architecture & $(3, 9, 2, 7, 7)$ & Maximum direct player contest without production depth; competitive dexterity with genuine strategic ergodicity \\
G3: Deep-Architecture Highly-Forgiving & $(2, 5, 8, 6, 8)$ & Le Havre depth but recoverable mistakes; a deep Euro where errors do not cascade to elimination \\
G4: High-Elegance High-Range Abstract & $(3, 6, 2, 9, 9)$ & Maximally elegant and maximally ergodic; Dominion approaches this (low I), Codenames approaches this (low R) \\
\hline
\end{tabular}
\end{table}

The nearest existing corpus game to each gap centre confirms the regions are genuinely
sparse: G1's nearest neighbour is CRUCIBLE at distance 4.1; G2's nearest is Crokinole at
3.8; G3's nearest is Concordia at 4.2; G4's nearest is Codenames at 3.1.

\subsection{Expert Validation}

Five experienced game designers (each with $\geq 2$ published titles) evaluated
natural-language design briefs derived from each gap. Table~\ref{tab:validation}
reports commercial-viability ratings (1--5 scale) and unexplored assessments.

\begin{table}[h]
\centering
\caption{Expert panel ratings for four design gap briefs.}
\label{tab:validation}
\begin{tabular}{lrrrl}
\hline
\textbf{Gap} & \textbf{Mean rating} & \textbf{Unexplored} & \textbf{Status} \\
\hline
G1: High-Tension Elegant Light & 4.2 & 5/5 & \textbf{Validated} \\
G2: High-Interaction Low-Architecture & 3.8 & 4/5 & \textbf{Validated} \\
G3: Deep-Architecture Highly-Forgiving & 3.1 & 2/5 & Not validated \\
G4: High-Elegance High-Range Abstract & 4.0 & 4/5 & \textbf{Validated} \\
\hline
\end{tabular}
\end{table}

Three of four gaps ($75\%$) meet the pre-registered validation threshold (mean rating
$\geq 3.5$ and $\geq 3$ of 5 designers assessing as unexplored). G3 fails because
three designers independently cited Terraforming Mars as occupying similar coordinates,
suggesting that the deep-forgiving Euro region is not as empty as the corpus implies
--- the corpus under-samples complex cooperative games.

For G1, designers noted that the tension-elegance combination is commercially attractive
(``this would be a premium filler at \$20'') and that existing push-your-luck games
(Can't Stop, Skull) either sacrifice elegance under tension or sacrifice tension in
favour of range. For G4, designers identified the combinatorial depth without complexity
as the hardest technical design challenge: ``you need a Dominion-level decision tree
but with Codenames-level onboarding, which is an unsolved problem.''

\subsection{TIGER Coordinates for All 20 Validation Games}

Full TIGER profiles for all 20 validation games are presented in
Table~\ref{tab:full-profiles} for reference.

\begin{table}[h]
\centering
\caption{TIGER profiles for 20 validation games (rounded to one decimal).}
\label{tab:full-profiles}
\begin{tabular}{lrrrrr}
\hline
\textbf{Game} & $T$ & $I$ & $G$ & $E$ & $R$ \\
\hline
Codenames       & 2.8 & 5.9 & 1.9 & 8.4 & 7.4 \\
Crokinole       & 6.1 & 8.3 & 1.6 & 9.1 & 4.7 \\
Love Letter     & 4.7 & 6.0 & 2.2 & 8.9 & 5.4 \\
Skull           & 5.8 & 7.1 & 2.0 & 8.0 & 5.2 \\
Hanabi          & 4.2 & 5.3 & 3.1 & 8.2 & 6.8 \\
Can't Stop      & 5.1 & 5.0 & 3.1 & 8.2 & 6.1 \\
Hive            & 4.3 & 5.6 & 3.8 & 7.9 & 5.9 \\
Pandemic        & 6.8 & 7.1 & 4.5 & 7.2 & 6.3 \\
Chess           & 7.3 & 6.5 & 4.6 & 7.4 & 7.0 \\
Catan           & 5.4 & 7.2 & 4.3 & 6.1 & 5.9 \\
Secret Hitler   & 6.9 & 5.4 & 4.7 & 6.3 & 6.3 \\
HAUL            & 5.3 & 5.8 & 5.7 & 6.5 & 4.9 \\
Agricola        & 7.4 & 4.2 & 7.1 & 4.8 & 7.8 \\
Brass: Birmingham & 6.5 & 5.9 & 7.8 & 5.1 & 7.2 \\
Spirit Island   & 7.1 & 6.2 & 7.3 & 4.6 & 7.1 \\
CRUCIBLE        & 7.0 & 5.8 & 6.9 & 5.4 & 7.5 \\
Azul            & 4.3 & 4.9 & 4.8 & 7.8 & 6.2 \\
Dominion        & 3.2 & 3.4 & 5.6 & 7.4 & 7.3 \\
7 Wonders       & 3.7 & 3.8 & 5.4 & 7.1 & 7.1 \\
Concordia       & 3.5 & 4.7 & 5.4 & 7.0 & 6.6 \\
\hline
\end{tabular}
\end{table}
