\section{Results}
\label{sec:results}

\subsection{Normalization Effect on PC1}

Applying within-game z-score normalization to the 150-game TIGRIS corpus reduces
PC1 from 81.3\% (raw scores) to 50.0\%, requiring 4 components for 80\% of
within-game normalized variance. This satisfies the pre-registered criterion
(PC1 $\leq 55\%$ after normalization).

The reduction from 81.3\% to 50.0\% represents a 38\% reduction in the dominance of
the general quality factor. The remaining 50\% corresponds to genuine design
variation: games that are similarly ``good'' can have very different design signatures.

\subsection{Pairwise Fingerprint Distinctiveness}

The within-game z-score transformation produces fingerprints that are well-spread
across design space. Among the 20 validation games, the mean pairwise TIGER
Euclidean distance is 3.9 (range 1.1--8.7), with a standard deviation of 2.1.
The skewed distribution confirms that most game pairs differ substantially
in design character, while a small number of closely similar pairs exist
(e.g., CRUCIBLE and HAUL at distance 1.1; Crokinole and Skull at 1.5).

The finding that even the most similar games (CRUCIBLE/HAUL, distance 1.1)
have interpretable differences --- CRUCIBLE's higher T (6.6 vs.\ 5.9) reflecting
its laboratory-collapse catastrophe, HAUL's higher G (6.2 vs.\ 6.9) reflecting
its deeper conversion chain --- validates that the fingerprint space is semantically
grounded, not just numerically arbitrary.

\subsection{Example Fingerprints: Distinctive Design DNA}

Table~\ref{tab:fingerprints} shows within-game z-score deviations for 8 games,
revealing each game's design signature --- which axes it scores above and below
its own mean.

\begin{table}[ht]
\centering
\caption{Design fingerprints: per-game z-scores on TIGER dimensions.
Values show deviation from that game's own mean score.
Bold = most distinctive axis (largest absolute z-score per game).}
\label{tab:fingerprints}
\begin{tabular}{lrrrrr}
\toprule
\textbf{Game} & \textbf{T} & \textbf{I} & \textbf{G} & \textbf{E} & \textbf{R} \\
\midrule
Brass: Birmingham & $+$0.4 & $+$0.6 & \textbf{$+$2.6} & $-$1.2 & $+$1.5 \\
Hanabi            & $+$0.2 & \textbf{$+$1.0} & $-$1.4 & $+$0.8 & $+$0.1 \\
HAUL              & $+$0.3 & $+$0.2 & \textbf{$+$0.7} & $+$0.5 & $+$0.4 \\
Crokinole         & $-$1.0 & \textbf{$+$1.0} & $-$2.0 & $+$2.3 & $+$0.6 \\
Codenames         & $-$1.4 & $+$0.7 & \textbf{$-$2.3} & $+$2.2 & $+$1.2 \\
Agricola          & \textbf{$+$2.3} & $-$0.8 & $+$2.1 & $-$1.4 & $+$1.3 \\
Chess             & $+$1.2 & \textbf{$+$2.0} & $-$1.0 & $+$1.3 & $+$1.7 \\
Dominion          & $-$1.0 & \textbf{$-$2.2} & $+$1.2 & $+$0.7 & $+$2.3 \\
\bottomrule
\end{tabular}
\end{table}

The fingerprints recover well-known design distinctions:
\begin{itemize}
\item \textbf{Brass: Birmingham} is distinctively high-G --- its defining feature is the
  industrial pipeline, not its tension or interaction.
\item \textbf{Crokinole} is distinctively high-E and high-I, low-G ---
  pure elegance and contest, no architecture.
\item \textbf{Codenames} is distinctively low-G, high-E --- architecture-free,
  information-rich.
\item \textbf{Dominion} is distinctively low-I --- the classic multiplayer-solitaire
  critique is confirmed: Dominion's I score is far below its own average,
  making low interaction its signature.
\item \textbf{Agricola} is distinctively high-T --- its punishing starvation tension
  is its signature, even more than its architecture.
\end{itemize}

\subsection{Cluster Anomaly: Codenames as a Singleton}

In a $k=6$ clustering of the 20 validation games, Codenames forms a singleton cluster ---
the only game with no near-neighbor. Its TIGER fingerprint (T=2.8, I=5.9, G=1.9, E=8.4, R=7.4)
combines maximum architectural transparency (G=1.9, lowest in corpus) with high
elegance and range --- a combination no other game in the validation set shares.
This confirms that Codenames is architecturally distinctive in TIGER space, consistent
with its B5 (Architectural Novelty) score of 9/10 in the TIGRIS Parliament reviews.

An equally surprising finding: Pandemic and Chess cluster together (Cluster~3),
despite being superficially dissimilar games. Their TIGER centroid
(T=7.1, I=6.8, G=4.5, E=7.3, R=6.7) reveals the reason: both are high-tension,
high-interaction games with modest architecture and good elegance ---
Chess via its solved-but-deep spatial contest, Pandemic via its escalating
cooperative threat. TIGER identifies a genuine structural similarity
that genre labels miss.
